Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-06-03 main.Rmd
choosing harmony section update

\noindent The harmony pairs could be arranged from highest to lowest average maximum pairwise distances across different levels of the cyclic granularities. But maximum is not robust to the number of levels and seems to be higher for harmonies with higher levels. Thus these maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels. \noindent The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process. Suppose $X_{1},X_{2}\ldots ,X_{n}$  be a sequence of independent and identically-distributed random variables, and $M_{n}=\max\{X_{1},\ldots ,X_{n}\}$. If a sequence of pairs of real numbers $a_{n}>0$ and $\lim _{{n\to \infty }}P\left({\frac  {M_{n}-b_{n}}{a_{n}}}\leq x\right)=F(x)$, where $F$ is a non-degenerate distribution function, then the limit distribution $F$ belongs to either the Gumbel, the Fréchet or the Weibull family. The normalizing constants, however, vary depending on the underlying distribution of $X_i$'s. Hence to normalize appropriately, it is important to assume a distribution of distances in our case.

@@

**Input** $(C_i, C_j, v) \quad \forall i, j \in N_C$  
**Output** MMPD (Median Maximum Pairwise Distances) measuring the average variation across different levels of $C_i$ and $C_j$ $\forall i, j \in N_C$

1. Fix $k$. Then there are $L$ groups corresponding to level $A_k$ of $C_i$ for the pair $(C_i, C_j)$.

@@

5. Use Step 1-4 to compute normalised maximum distance for each $k$ levels ($NM_k$).

6. Compute median maximum pairwise distance $$MMPD = median\{NM_1, NM_2, \dots, NM_K\}$$.

7. Repeat Step 1 to 6 for all harmony pairs.

>>>>

\noindent The harmony pairs could be arranged from highest to lowest average maximum pairwise distances across different levels of the cyclic granularities. But maximum is not robust to the number of levels and seems to be higher for harmonies with higher levels. Thus these maximum pairwise distances need to be normalized for different harmonies in a way that eliminates the effect of different levels. \noindent The Fisher–Tippett–Gnedenko theorem in the field of Extreme Value Theory states that the maximum of a sample of iid random variables after proper re-normalization can converge in distribution to only one of Weibull, Gumbel or Freschet distribution, independent of the underlying data or process. Suppose $d_{1},d_{2}\ldots ,d_{m}$  be a sequence of independent and identically-distributed pairwise distances, and $M_{m}=\max\{d_{1},\ldots ,d_{m}\}$. If a sequence of pairs of real numbers $a_{m}>0$ and $\lim _{{n\to \infty }}P\left({\frac  {M_{m}-b_{m}}{a_{m}}}\leq x\right)=F(x)$, where $F$ is a non-degenerate distribution function, then the limit distribution $F$ belongs to either the Gumbel, the Fréchet or the Weibull family. The normalizing constants, however, vary depending on the underlying distribution of $d_i$'s. Hence to normalize appropriately, it is important to assume a distribution of $d_i$'s in our case.

@@

- **Input:** Data corresponding to all harmony pairs, i.e., data sets of the form $(C_i, C_j, v)$ 
$\forall i, j \in N_C$  
- **Output:** MMPD (Median Maximum Pairwise Distances) measuring the average variation across different levels of $C_i$ and $C_j$ $\forall i, j \in N_C$

1. Fix $k$. Then there are $L$ groups corresponding to level $A_k$ of $C_i$.

@@

5. Use Steps 1-4 to compute normalised maximum distance for each $k$ levels ($NM_k$).

6. Compute $MMPD = median(NM_1, NM_2, \dots, NM_K)/log(K)$. Median normalised distance grows at the rate of log(K) as $K\rightarrow\infty$ and hence is normalised for the value of K in $MMPD$.

7. Repeat Steps 1 to 6 for all harmony pairs.
